### 2019-02-04 thesis_report/results.tex
done with results.tex

		\subsection{Estimation of the gap through momentum cutoff}
			As explained in the Methods chapter, we estimate the topological gap using a quasiclassical estimate.
			We keep the ratio $4\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.
			In Figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
			Note that the quasi-classics are only valid once the zigzag cuts off all trajectories which extend infinitely.
			Also important to note is that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Fig.~\ref{fig:longest_trajectory_wo_corners}

@@

			We conclude that the proposed model to estimate the gap does not capture the physics of the zigzag very well: the model merely gives a lower bound for the topological gap.

>>>>

		\subsection{Estimation of the gap through momentum cutoff}
			As explained in chapter \ref{chap:methods}, we estimate the topological gap using a quasiclassical estimate.
			We keep the ratio $4\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.
			In figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
			Note that the quasi-classics are only valid once the zigzag cuts off all trajectories which extend infinitely.
			Also important to note is that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Fig.~\ref{fig:longest_trajectory_wo_corners}

@@

			We conclude that the proposed model to estimate the gap does not capture all the physics of the zigzag very well: the model merely gives a lower bound for the topological gap.
